Effect of character correlation

### 2017-09-26 Analysis/EffectCorrelationStats.Rmd
Updated stats

@@

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm)
metric.labels <- c("RF", "", "Tr", "")
test_table <- pair.test.table(methods_list, metric.label = metric.labels)
```

@@

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)

## Tables
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_Tr_best, row.names = FALSE, digit = 3)
```

>>>>

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction)")

@@

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm)
metric.labels <- c("RF", "Tr")
test_table <- pair.test.table(methods_list, metric.label = metric.labels)
```

@@

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)
```
